Impacts of Social Backgrounds on People's Perception of the Risk of Getting AIDS

### 2022-04-11 outputs/paper/paper.Rmd
Update paper.Rmd

>>>>

### Collection Process
How was the data associated with each instance acquired?
- The data set was collected by the DHS program in Kenya. Details can be found in the Data Methodology section of the report.
What mechanisms or procedures were used to collect the data (e.g., hardware apparatuses or sensors, manual human curation, software programs, software APIs)?
- Household questionnaires, in-person interviews, and other types of model questionnaires were employed. 
If the dataset is a sample from a larger set, what was the sampling strategy (e.g., deterministic, probabilistic with specific sampling probabilities)?
- The enumeration areas are drawn from census files, and samples of households were selected from the enumeration areas.
Who was involved in the data collection process (e.g., students, crowdworkers, contractors) and how were they compensated (e.g., how much were crowdworkers paid)?
- The DHS program members were involved in the data collection process.
Over what timeframe was the data collected?
- The data used in this report was collected in 1998.
Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (e.g., websites)?
- The data is obtained from the official website of the DHS program. The link is https://dhsprogram.com/
Were the individuals in question notified about the data collection?
- The individuals of the question are well aware of the survey as well as the data collection.
Did the individuals in question consent to the collection and use of their data?
- The individuals in question have consented to the collection and use of their data.
If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses?
- There’s no open information available to tell if the consent for revokes were granted to the survey participants.
Has an analysis of the potential impact of the dataset and its use on data subjects (e.g., a data protection impact analysis) been conducted?
- The analysis of the original survey data was conducted by the National Council for Population and Development of the Republic of Kenya. The link to the report is: https://dhsprogram.com/pubs/pdf/FR102/FR102.pdf
Any other comments?
- None.

### Preprocessing/ cleaning/ labeling

Was any preprocessing/cleaning/labeling of the data done?
- The data was originally obtained in PDF format. The table from the survey PDF was converted to a usable data frame in R using the library pdftools for R. 
Was the “raw” data saved in addition to the preprocessed/cleaned/labeled data (e.g., to support unanticipated future uses)?
-The raw data obtained is saved in outputs/data/raw_data_male.csv and outputs/data/raw_data_female.csv
Is the software that was used to preprocess/clean/label the data available?
-R software is available at https://www.R-project.org/

### Uses
Has the dataset been used for any tasks already?
- The dataset has not been used for other tasks yet.
Is there a repository that links to any or all papers or systems that use the dataset?
- https://github.com/R300G/Kenya_Demographic_1998.git
What (other) tasks could the dataset be used for?
- The dataset would be used for understanding behavior to disease amongst different socio-economic demographic
Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses?
- The cleaning process is very specific to the way this table was formatted in the original PDF and may not work on other tables.
